A robust framework for variable extrusion width concentric toolpath generation

### 2019-07-13 4_method.tex
local maxima bead rounding  (First draft version)

>>>>

If a local maximum gets an odd bead count this would result in a single dot bead toolpath with zero length.
This not only forms an exception we would need to account for when extracting toolpath segments,
it also results in a toolpath which is difficult to manufacture.
Instead we prevent odd bead counts by either increasing or decresing the bead count based on the prefered widths of those bead counts:
if $v.B^* \% 2 = 1$ then $v.B^* := \argmin_n |p(n) - R(v)|$.
